PanGraph: scalable bacterial pan-genome graph construction \\ Supplementary Information

### 2022-09-07 supplementary.tex
feat: updated table

% TODO: also report average core genome size?
% TODO: evaluate core genome divergence? Or average mash triangle distance?
% TODO: avoid talking about PanX?
% TODO: add link with accesion numbers and download?

\begin{table}[hb]
    \begin{tabular}{l l l l}
        \hline\hline
        Species         & N. isolates & Avg. chromosome length [Mbp] & Avg. pairwise divergence (core genes) \\
        \hline
        E.~Coli         & 307         & 5.0                          &                                       \\
        K.~Pneumoniae   & 109         & 5.3                          &                                       \\
        H.~Pylori       & 85          & 1.6                          &                                       \\
        M.~Tuberculosis & 51          & 4.4                          &                                       \\
        P.~Marinus      & 10          & 1.8                          &                                       \\
        \hline
    \end{tabular}
    \caption{{\bf Dataset overview}. We downloaded complete chromosome sequences from RefSeq for 5 different bacterial species. For each species we report the number of isolates downloaded, along with the average chromosome length and average pairwise divergence on core genes.}
    \label{table:panx-dataset}
\end{table}

>>>>

% TODO: describe incuded quantitites better, and the dataset characteristics.
% TODO: decide what to include.
% TODO: add link with accesion numbers and download?
% TODO: double-check numbers

\begin{table}[hb]
    \begin{tabular}{l l l l l l}
        \hline\hline
        Species         & N. isolates & $\avg{l}$ [Mbp] & $\avg{d}$ & $f_p$  & $f_g$  \\
        \hline
        E.~Coli         & 307         & 5.0             & 1.6\%     & 3.7\%  & 15.4\% \\
        K.~Pneumoniae   & 109         & 5.3             & 0.8\%     & 17.4\% & 46.5\% \\
        H.~Pylori       & 85          & 1.6             & 4.2\%     & 30.2\% & 42.2\% \\
        M.~Tuberculosis & 51          & 4.4             & 0.03\%    & 57.9\% & 61.7\% \\
        P.~Marinus      & 10          & 1.8             & 24.3\%    & 21.0\% & 45.6\% \\
        \hline
    \end{tabular}
    \caption{{\bf Dataset overview}. We downloaded complete chromosome sequences from RefSeq for 5 different bacterial species. For each species we report the number of isolates downloaded, along with the average chromosome length $\avg{l}$, average pairwise divergence on core genes $\avg{d}$, fraction of core pangenome $f_p$ and fraction of core genome $f_g$. $f_p$ is the fraction of core gene cluster over the total (weighted by length), while $f_g$ is the average fraction of core genes in a genome (weighted by length).}
    \label{table:panx-dataset}
\end{table}
